---
title: "Sim1 — hierarchical item-level model"
date: "2026-08-28"
output: html_document
---

Companion to `Sim1.Rmd`: fits the hierarchical long-format ordinal model specified in `methods/claude_ordinal_model_proposal.md` on the same simulations.

The model, in the notation of the proposal:

$$P(Y_{itj} \ge k) = \mathrm{logit}^{-1}(\eta_{itj} - \kappa_{j,k}), \qquad
\eta_{itj} = a_i + a_{ij} + \omega_{it} + (\beta_j + b_i + b_{ij} + \gamma\, g_i)\, s_{it}$$

Correspondence to the brms formula below: `(1 + time | subject_id)` gives $(a_i, b_i)$, `(1 + time | subject_id:item)` gives $(a_{ij}, b_{ij})$, `(1 | subject_id:visit_id)` gives $\omega_{it}$, `0 + item:time` gives $\beta_j$, `time_treat` gives $\gamma$, and `thres(4, gr = item)` gives the item-specific thresholds $\kappa_{j,k}$.

The chunks from "Long-format data" onward only need `sims`, `args_sh`, `cache_dir`, `questions_to_fit` in scope, so they can be pasted directly into `Sim1.Rmd` to run on the identical replicates. Run standalone, this file regenerates `sims` with the same seed.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(purrr)
library(tidyr)
library(readr)
library(ggplot2)
library(brms)
library(ggdist)
library(cmdstanr)
library(patchwork)

options(mc.cores = parallel::detectCores(), brms.backend = "cmdstanr")
cache_dir <- here::here("local_temp_data", "simulation_test")
if(!dir.exists(cache_dir)) {
  dir.create(cache_dir, recursive = TRUE)
}

source(here::here("R", "data_prep.R"))
source(here::here("R", "simulate_data.R"))
source(here::here("R", "effect_functions.R"))
source(here::here("R", "sampling_parallel.R"))
source(here::here("R", "brm_parallel.R"))
source(here::here("R", "cluster.R"))

setup_cluster(max_server_workers = 100)
```

```{r}
#LOAD DATA
proact <- read_csv(here::here("private_data/F_PROACT_ALSFRS.csv"))
proact_standardized <- data_prep(proact)
```

## Simulate data

```{r}
# SIMULATION SCENARIO (identical to Sim1.Rmd)
nsims = 1
n_subj_per_group <- 50
eff_probs <- rep(0.5, times = nsims)
question_col_names <- sprintf("Q%02d", 1:12)
questions_to_fit <- question_col_names

args_sh = list(adapt_delta = 0.95,
               init = 0.1,
               chains = 3,
               iter = 3000,
               warmup = 1000)
```

```{r}
# SIMULATE DATA
set.seed(468652233)

sims <- list()
for(i in 1:length(eff_probs)) {
    sims[[i]] <- simulate_data_from_registry(proact_standardized,
                                             max_duration = 12,
                                             min_measurements_per_subject = 4,
                                             max_measurements_per_subject = 8,
                                             n_subjects_per_group = n_subj_per_group,
                                             effect_prob = eff_probs[i])
}
```

## Long-format data

One row per subject x visit x item. `score` is shifted to 1..5 (brms requirement), `item` is a factor (defines the threshold groups), and the treatment-by-time column is precomputed so that its coefficient has a stable name (`time_treat`) for priors and summaries.

```{r}
prepare_long_data <- function(sim_data, questions = questions_to_fit) {
    sim_data %>%
        select(subject_id, visit_id, group, alsfrs_dly_mnths, all_of(questions)) %>%
        pivot_longer(all_of(questions), names_to = "item", values_to = "score") %>%
        mutate(score = score + 1,
               item = factor(item, levels = questions),
               treat = as.integer(group == "Treatment"),
               time = alsfrs_dly_mnths,
               time_treat = time * treat)
}

args_per_fit_long <- purrr::map(sims, ~ list(data = prepare_long_data(.x)))
```

## Hierarchical model

In brms ordinal formulas the intercept is implicit and *is* the thresholds, so no item main effects are included, the grouped thresholds absorb them. `item:time` (interaction only, no `time` main effect) gives each item its own population rate; there is a single pooled treatment effect on the latent rate.

```{r}
hier_formula <- bf(
    score | thres(4, gr = item) ~
        item:time + time_treat + #the same as time*treat 
        (1 + time | subject_id) +
        (1 + time | subject_id:item) +
        (1 | subject_id:visit_id),
    family = cumulative("logit")
)

hier_priors <- c(
    prior(normal(0, 10), class = "Intercept"),
    prior(normal(0, 1), class = "b"),
    prior(normal(0, 0.3), class = "b", coef = "time_treat"),
    prior(student_t(3, 0, 2.5), class = "sd"),
    prior(normal(0, 1), class = "sd", coef = "time", group = "subject_id"),
    prior(normal(0, 1), class = "sd", coef = "time", group = "subject_id:item"),
    prior(normal(0, 1), class = "sd", group = "subject_id:visit_id"),
    prior(lkj(2), class = "cor")
)
```

```{r}
# Treatment - Control difference in the change of the expected ALSFRS-R total
# between month 0 and s_star, computed two ways from the long-format fit:
#   effect_samples          - all random effects set to zero (re_formula = NA);
#                             the same conditional estimand as effect_from_sim_study,
#                             kept for continuity with the existing pipeline.
#   effect_samples_marginal - random effects integrated out by predicting for n_new
#                             fresh subjects per posterior draw (sample_new_levels =
#                             "gaussian"); this is the population-averaged quantity
#                             that matches the plasmode ground truth and the LMM
#                             estimand, at the cost of a little Monte Carlo noise.
# Runs inside worker sessions, hence the explicit :: prefixes and base R only.
effect_hier_from_sim_study <- function(fit, s_star = 12,
                                       n_new = 100, ndraws_marginal = 1000) {
    items <- levels(fit$data$item)

    expected_total <- function(pred, keys, denom = 1) {
        cats <- as.integer(dimnames(pred)[[3]])
        esc <- 0
        for (k in seq_along(cats)) {
            esc <- esc + pred[, , k] * cats[k]
        }
        out <- sapply(unique(keys), function(kk) {
            rowSums(esc[, keys == kk, drop = FALSE]) / denom
        })
        out
    }
    did <- function(tot, s_star) {
        (tot[, paste0(s_star, "_1")] - tot[, "0_1"]) -
            (tot[, paste0(s_star, "_0")] - tot[, "0_0"])
    }

    ## conditional (median-patient) version
    nd_cond <- expand.grid(item = factor(items, levels = items),
                           time = c(0, s_star), treat = c(0, 1),
                           KEEP.OUT.ATTRS = FALSE)
    nd_cond$time_treat <- nd_cond$time * nd_cond$treat
    pe <- brms::posterior_epred(fit, newdata = nd_cond, re_formula = NA)
    eff_cond <- did(expected_total(pe, paste(nd_cond$time, nd_cond$treat, sep = "_")),
                    s_star)

    ## marginal (population-averaged) version
    nd_marg <- expand.grid(subject_id = paste0("new_", seq_len(n_new)),
                           item = factor(items, levels = items),
                           time = c(0, s_star), treat = c(0, 1),
                           KEEP.OUT.ATTRS = FALSE)
    nd_marg$time_treat <- nd_marg$time * nd_marg$treat
    nd_marg$visit_id <- paste(nd_marg$subject_id, nd_marg$time, sep = "_")
    pm <- brms::posterior_epred(fit, newdata = nd_marg, re_formula = NULL,
                                allow_new_levels = TRUE,
                                sample_new_levels = "gaussian",
                                ndraws = ndraws_marginal)
    eff_marg <- did(expected_total(pm, paste(nd_marg$time, nd_marg$treat, sep = "_"),
                                   denom = n_new),
                    s_star)

    n_divergent <- sum(rstan::get_divergent_iterations(fit$fit))
    ss <- posterior::summarise_draws(posterior::as_draws(fit))

    list(
        effect_samples = eff_cond,
        effect_samples_marginal = eff_marg,
        gamma_samples = as.vector(posterior::extract_variable(
            posterior::as_draws(fit), "b_time_treat")),
        diags = data.frame(n_divergent,
                           max_rhat     = max(ss$rhat,     na.rm = TRUE),
                           min_ess_bulk = min(ss$ess_bulk, na.rm = TRUE),
                           min_ess_tail = min(ss$ess_tail, na.rm = TRUE))
    )
}
```

```{r}
summary_hier <- brm_parallel(
    args_shared = c(list(formula = hier_formula, prior = hier_priors), args_sh),
    args_per_fit = args_per_fit_long,
    cache_dir = cache_dir,
    cache_fits = FALSE,
    cache_summaries = TRUE,
    summarise_fun = effect_hier_from_sim_study,
    future.globals = list("effect_hier_from_sim_study" = effect_hier_from_sim_study))

effects_hier <- purrr::map_df(1:length(eff_probs),
    ~ data.frame(id = .x, type = "hier", eff_prob = eff_probs[.x],
                 estimate = summary_hier[[.x]]$effect_samples))

effects_hier_marg <- purrr::map_df(1:length(eff_probs),
    ~ data.frame(id = .x, type = "hier_marginal", eff_prob = eff_probs[.x],
                 estimate = summary_hier[[.x]]$effect_samples_marginal))
```

## Secondary model: item-specific treatment effects

The pooled `time_treat` is the primary analysis. The secondary variant lets the effect vary by item, hierarchically shrunk toward the pooled value: `(0 + time_treat | item)` is exactly $\gamma_j = \gamma + u_j$, $u_j \sim N(0, \tau_\gamma^2)$.

```{r}
hier_formula_itemfx <- bf(
    score | thres(4, gr = item) ~
        item:time + time_treat +
        (0 + time_treat | item) +
        (1 + time | subject_id) +
        (1 + time | subject_id:item) +
        (1 | subject_id:visit_id),
    family = cumulative("logit")
)

hier_priors_itemfx <- c(
    hier_priors,
    prior(normal(0, 0.15), class = "sd", group = "item")
)

summary_hier_itemfx <- brm_parallel(
    args_shared = c(list(formula = hier_formula_itemfx, prior = hier_priors_itemfx), args_sh),
    args_per_fit = args_per_fit_long,
    cache_dir = cache_dir,
    cache_fits = FALSE,
    cache_summaries = TRUE,
    summarise_fun = effect_hier_from_sim_study,
    future.globals = list("effect_hier_from_sim_study" = effect_hier_from_sim_study))

effects_hier_itemfx <- purrr::map_df(1:length(eff_probs),
    ~ data.frame(id = .x, type = "hier_itemfx", eff_prob = eff_probs[.x],
                 estimate = summary_hier_itemfx[[.x]]$effect_samples))
```

## Calibration summary

At `eff_prob = 0.5` the strong null holds exactly (the within-pair assignment is a fair coin), so rejection rates here are type I error and interval coverage of 0 is directly interpretable.

```{r}
summarise_effects <- function(effects_df) {
    effects_df %>%
        group_by(type, eff_prob, id) %>%
        summarise(mean_est = mean(estimate),
                  lower95 = quantile(estimate, 0.025),
                  upper95 = quantile(estimate, 0.975),
                  reject = lower95 > 0 | upper95 < 0,
                  .groups = "drop") %>%
        group_by(type, eff_prob) %>%
        summarise(n_fits = n(),
                  mean_estimate = mean(mean_est),
                  sd_estimate = sd(mean_est),
                  type_I_or_power = mean(reject),
                  mc_se_rejection = sqrt(type_I_or_power * (1 - type_I_or_power) / n_fits),
                  .groups = "drop")
}

bind_rows(effects_hier, effects_hier_marg, effects_hier_itemfx) %>%
    summarise_effects()

collect_diags_all(list(hier = summary_hier, hier_itemfx = summary_hier_itemfx)) %>%
    summarise_diags()
```

```{r}
# Conditional vs marginal estimand, per replicate: the conditional (median-patient)
# version is systematically larger in magnitude because it evaluates the expected-score
# curve at its steepest point; the marginal version is the one comparable to the LMM
# and to the plasmode ground truth.
inner_join(
    effects_hier %>% group_by(id) %>% summarise(conditional = mean(estimate)),
    effects_hier_marg %>% group_by(id) %>% summarise(marginal = mean(estimate)),
    by = "id") %>%
    ggplot(aes(conditional, marginal)) +
    geom_point() +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
    theme_minimal()
```

## 
