---
title: "simulations_logit_from_scratch"
author: "Michaela Krynická"
date: "2026-04-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(purrr)
library(tidyr)
library(readr)
library(ggplot2)
library(brms)
library(ggdist)
library(cmdstanr)
library(patchwork)
library(splines)

# OPTIMIZE PERFORMANCE 
options(mc.cores = parallel::detectCores(), brms.backend = "cmdstanr")
cache_dir <- here::here("local_temp_data", "simulation_test")
if(!dir.exists(cache_dir)) {
  dir.create(cache_dir, recursive = TRUE)
}

source(here::here("R", "simulate_data.R"))
source(here::here("R", "sampling_parallel.R"))
source(here::here("R", "brm_parallel.R"))
source(here::here("R", "cluster.R")) #set up future package 

#LOAD DATA
proact <- read_csv(here::here("private_data/F_PROACT_ALSFRS.csv"))
```

```{r}
setup_cluster(max_server_workers = 100)
```

## Data preparation

```{r}
# DATA PREPARATION
# unify Q5
# omit vars that are not useful
# unify question names
# keep only complete obs

days_per_month <- 365.25 / 12

any(!is.na(proact$Q5a_Cutting_without_Gastrostomy) & !is.na(proact$Q5b_Cutting_with_Gastrostomy) &
      proact$Q5a_Cutting_without_Gastrostomy != proact$Q5b_Cutting_with_Gastrostomy)
#TODO: need to resolve this

proact_full <- proact %>% 
    mutate(Q5_Cutting_Combined = if_else(is.na(Q5a_Cutting_without_Gastrostomy), 
                                         Q5b_Cutting_with_Gastrostomy, Q5a_Cutting_without_Gastrostomy)) %>%
    select(-Q5b_Cutting_with_Gastrostomy, -Q5a_Cutting_without_Gastrostomy, 
           -Q10_Respiratory, -ALSFRS_Total, -Mode_of_Administration, -ALSFRS_Responded_By) %>%
    filter(if_all(c(starts_with("Q"), starts_with("R")), function(x) { !is.na(x) } )) 


question_col_names_proact <- sort(names(proact_full)[grepl("^[QR]", names(proact_full))])
question_col_names <- sprintf("Q%02d", 1:12)
question_col_names_translation <- sprintf("Q%02d", 1:12)
names(question_col_names_translation) <- question_col_names_proact

proact_standardized <- proact_full %>%
    rename_with(function(x) { question_col_names_translation[x]}, .cols = all_of(question_col_names_proact)) %>%
    rename(alsfrs_total = ALSFRS_R_Total) %>%
    mutate(alsfrs_dly_mnths = ALSFRS_Delta / days_per_month) %>%
    select(subject_id, all_of(question_col_names), alsfrs_total, alsfrs_dly_mnths) 


proact_standardized
```

## Simulate data

```{r}

# SIMULATION SCENARIO
nsims = 100
nsims_sub <- 100 #size for subsample for testing the models
n_subjects_per_group <- 50
eff_probs <- rep(c(0.5, 0.7, 0.8), times = nsims) # define the no. of simulations here 
eff_prob <- eff_probs[seq(from = 1, to = length(eff_probs), by = 3)][1:nsims_sub]  # only 0.5
```

```{r}

# SIMULATE DATA 
#set.seed(468652233)
set.seed(234)

sims <- list()
for(i in 1:length(eff_probs)) {
  sims[[i]] <- simulate_data_from_registry(proact_standardized,
                                    max_duration = 12,
                                    min_measurements_per_subject = 4,
                                    max_measurements_per_subject = 8,
                                    n_subjects_per_group = n_subjects_per_group,
                                    effect_prob = eff_probs[i])
  if(i <= 15) {
  print(sims[[i]] %>% ggplot(aes(x = alsfrs_dly_mnths, y = alsfrs_total - alsfrs_start, group = subject_id,
                                color = group)) +
    geom_line(position = position_jitter(height = 0.3), alpha = 0.5) + ggtitle(paste0("Eff prob: ", eff_probs[i]))) 
  }
}

```

## Default priors & One question

```{r}

# CHOOSE ONLY SUBSAMPLE OF DATASETS WITH EFF_PROB = 0.5
sims_null <- sims[seq(from = 1, to = length(sims), by = 3)][1:nsims_sub] 

#CHECK THE SCORE DISTRIBUTION OF THE CHOSEN QUESTION
question_to_fit <- question_col_names[c(1)] #change the no. of questions here 

sim_scores <- purrr::map_dfr(sims_null,
                              ~ as.list(summary(as.factor(.x[[question_to_fit]]))),
                              .id = "sim_id") %>% 
    select(-sim_id) %>% 
    summarise(across(everything(), mean))

sim_scores
```

### Logit model

```{r}

#RANDOM INTERCEPT 
formula_text <- paste0(question_to_fit, " ~ 1 + alsfrs_dly_mnths * group + (1 | subject_id)")

logit_formula <- as.formula(formula_text)

args_per_fit <- list()
for(i in 1:length(sims_null)) {
  data_for_fit <- sims_null[[i]] %>%
  mutate(across(all_of(question_col_names), function(x) { x + 1 }))
  args_per_fit[[i]] <- list(data = data_for_fit)
}


#RANDOM SLOPE
formula_text_rslope <- paste0(question_to_fit, " ~ 1 + alsfrs_dly_mnths * group + (1 + alsfrs_dly_mnths | subject_id)")

logit_formula_rslope <- as.formula(formula_text_rslope)


```

```{r}

#RANDOM INTERCEPT
fits_logit <- brm_parallel(
    args_shared = list(formula = bf(logit_formula, family = cumulative()), #+ set_rescor(FALSE), not applicable, we have one question only 
                                    adapt_delta = 0.95,
                                    init = 0.1,
                                    chains = 4,
                                    iter = 3000,
                                    warmup = 1000),
    args_per_fit = args_per_fit,
    cache_dir = cache_dir,
    cache_fits = TRUE,
    future.globals = FALSE)

#RANDOM SLOPE
fits_logit_rslope <- brm_parallel(
    args_shared = list(formula = bf(logit_formula_rslope, family = cumulative()), #+ set_rescor(FALSE), not applicable, we have one question only 
                                    adapt_delta = 0.95,
                                    init = 0.1,
                                    chains = 4,
                                    iter = 3000,
                                    warmup = 1000),
    args_per_fit = args_per_fit,
    cache_dir = cache_dir,
    cache_fits = TRUE,
    future.globals = FALSE)

```

```{r}

#FUNCTION FOR THE LOGIT EFFECTS 
#(the only change in the original function is the -1 in the col_values)
effects_logit <- function(fit) {
  predict_data <- data.frame(group = c("Control", "Control", "Treatment", "Treatment"),
                             alsfrs_dly_mnths = c(0, 12, 0, 12))
  
  pred <- posterior_epred(fit, newdata = predict_data, re_formula = NA)
  
  expected_sum <- function(x) {
    col_values <- as.integer(colnames(x)) - 1 #back to the real values of the categories
    multiplied <- sweep(x, MARGIN = 2, STATS = col_values, FUN = "*")
    rowSums(multiplied)
  }
  
  start_control <- expected_sum(pred[,1,])
  end_control <- expected_sum(pred[,2,])
  start_treatment <- expected_sum(pred[,3,])
  end_treatment <- expected_sum(pred[,4,])
  
  (end_treatment - start_treatment) - (end_control - start_control)
}

```

```{r}

#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 
all_effects_logit <- purrr::map_df(1:length(eff_prob), #change length eff_probs here
                             ~ data.frame(id = .x, type = "logit", eff_prob = eff_prob[.x], estimate = effects_logit(fits_logit[[.x]])))

#RANDOM SLOPE
 all_effects_logit_rslope <- purrr::map_df(1:length(eff_prob), #change length eff_probs here
                             ~ data.frame(id = .x, type = "logit_rslope", eff_prob = eff_prob[.x], estimate = effects_logit(fits_logit_rslope[[.x]])))

```

```{r}

#VISUALIZE THE EFFECTS 
plot_logit <- all_effects_logit %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id, y = estimate)) + 
    geom_hline(yintercept = 0) +
    stat_pointinterval(position = position_dodge(width = 0.3)) + 
    #expand_limits(y = shared_range) +
    ggtitle("Logit")
plot_logit


#RANDOM SLOPE
plot_logit_rslope <- all_effects_logit_rslope %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id, y = estimate)) + 
    geom_hline(yintercept = 0) +
    stat_pointinterval(position = position_dodge(width = 0.3)) + 
    #expand_limits(y = shared_range) +
    ggtitle("Logit")
plot_logit_rslope
```

### Lme4 checks

#### Simple

```{r}

# FIT SIMPLE LMER MODEL
fits_lmer_simple <- purrr::map(sims_null, function(data_for_lmer) {
  lme4::lmer(data_for_lmer[[question_to_fit]] ~ 1 + alsfrs_dly_mnths*group+ (1 |subject_id), data = data_for_lmer)
})

fits_lmer_simple_rslope  <- purrr::map(sims_null, function(data_for_lmer) {
  lme4::lmer(data_for_lmer[[question_to_fit]] ~ 1 + alsfrs_dly_mnths*group+ (1 + alsfrs_dly_mnths |subject_id), data = data_for_lmer)
})

```

```{r}

#FUNCTION FOR THE LMER SIMPLE EFFECTS 
effects_lmer_simple <- function(fit) {
  # Estimating conf ints. for a linear combination
  # Based on https://bookdown.org/ccolonescu/RPoE4/intervalest.html
  vc <- vcov(fit)
  
  lincomb <- rep(0, nrow(vc))
  names(lincomb) <- rownames(vc)
  lincomb["groupTreatment"] <- 1
  lincomb["alsfrs_dly_mnths:groupTreatment"] <- 12

  alpha <- c(0.5, 0.05)
  estimate <- as.numeric(lincomb %*% fit@beta)
  df <- df.residual(fit)
  tcr <- qt(1-alpha/2, df)
  estimate_se <- as.numeric(sqrt( lincomb %*% (vc %*% lincomb)))
  lower <- estimate - tcr*estimate_se
  upper <- estimate + tcr*estimate_se
  data.frame(estimate = estimate, lower95 = lower[2], lower50 = lower[1], upper50 = upper[1],
             upper95 = upper[2])
}

```

```{r}

# COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 
all_effects_lmer_simple <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_simple", eff_prob = eff_prob[.x], effects_lmer_simple(fits_lmer_simple[[.x]]))))

all_effects_lmer_simple_rslope <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_simple_rslope", eff_prob = eff_prob[.x], effects_lmer_simple(fits_lmer_simple_rslope[[.x]]))))

```

```{r}

# PLOT LMER SIMPLE 
plot_lmer_simple <- all_effects_lmer_simple %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 simple")

plot_lmer_simple

plot_lmer_simple_rslope <- all_effects_lmer_simple_rslope %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 simple_rslope")

plot_lmer_simple_rslope


```

\

#### Splines

```{r}

# FIT LMER SPLINES MODEL
get_spline_coeffs <- function(x) {
  res <- ns(x, knots = 6, Boundary.knots = c(0, 12))
  colnames(res) <- paste0("dly_mnths_spline_", 1:ncol(res))
  res
}

fits_lmer_splines <- purrr::map(sims_null, function(data_for_lmer) {
    
     spline_data <- ns(data_for_lmer$alsfrs_dly_mnths, 2)
         data_for_lmer <- cbind(data_for_lmer,
                           get_spline_coeffs(data_for_lmer$alsfrs_dly_mnths))
     
  lme4::lmer(data_for_lmer[[question_to_fit]] ~ 1 + dly_mnths_spline_1 * group
             + dly_mnths_spline_2 * group + (1 |subject_id), data = data_for_lmer)
})

fits_lmer_splines_rslope <- purrr::map(sims_null, function(data_for_lmer) {
    
     spline_data <- ns(data_for_lmer$alsfrs_dly_mnths, 2)
         data_for_lmer <- cbind(data_for_lmer,
                           get_spline_coeffs(data_for_lmer$alsfrs_dly_mnths))
     
  lme4::lmer(data_for_lmer[[question_to_fit]] ~ 1 + dly_mnths_spline_1 * group
             + dly_mnths_spline_2 * group + (1 + alsfrs_dly_mnths |subject_id), data = data_for_lmer)
})



```

```{r}

#FUNCTION FOR THE LMER SPLINES EFFECTS 
effects_lmer_splines <- function(fit) {
  # Estimating conf ints. for a linear combination
  # Based on https://bookdown.org/ccolonescu/RPoE4/intervalest.html
  vc <- vcov(fit)
  
  spline_coeffs_0 <- get_spline_coeffs(0)
  spline_coeffs_12 <- get_spline_coeffs(12)
  spline_coeffs_diff <- spline_coeffs_12 - spline_coeffs_0
  
  lincomb <- rep(0, nrow(vc))
  names(lincomb) <- rownames(vc)
  lincomb["groupTreatment"] <- 1
  lincomb["dly_mnths_spline_1:groupTreatment"] <- spline_coeffs_diff[1]
  lincomb["groupTreatment:dly_mnths_spline_2"] <- spline_coeffs_diff[2]
  
  alpha <- c(0.5, 0.05)
  estimate <- as.numeric(lincomb %*% fit@beta)
  df <- df.residual(fit)
  tcr <- qt(1-alpha/2, df)
  estimate_se <- as.numeric(sqrt( lincomb %*% (vc %*% lincomb)))
  lower <- estimate - tcr*estimate_se
  upper <- estimate + tcr*estimate_se
  data.frame(estimate = estimate, lower95 = lower[2], lower50 = lower[1], upper50 = upper[1],
             upper95 = upper[2])
}


```

```{r}

#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 
all_effects_lmer_splines <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_splines", eff_prob = eff_prob[.x], effects_lmer_splines(fits_lmer_splines[[.x]]))))

all_effects_lmer_splines_rslope <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_splines_rslope", eff_prob = eff_prob[.x], effects_lmer_splines(fits_lmer_splines_rslope[[.x]]))))
```

```{r}

#PLOT LMER SPLINES 
plot_lmer_splines <- all_effects_lmer_splines %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 splines")

plot_lmer_splines

plot_lmer_splines_rslope <- all_effects_lmer_splines_rslope %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 splines")

plot_lmer_splines_rslope


```

### Joined

```{r}

#JOINED PLOT
summarise_brms <- function(all_effects) {
  all_effects %>% group_by(type, eff_prob, id) %>%
    summarise(lower95 = quantile(estimate, 0.025),
              lower50 = quantile(estimate, 0.25),
              upper50 = quantile(estimate, 0.75),
              upper95 = quantile(estimate, 0.975),
              estimate = mean(estimate),
              .groups = "drop")
}

my_pos <- position_dodge(width = 0.5)

rbind(summarise_brms(all_effects_logit),
      summarise_brms(all_effects_logit_rslope),
      all_effects_lmer_splines,
      all_effects_lmer_splines_rslope,
      all_effects_lmer_simple,
      all_effects_lmer_simple_rslope) %>%
    mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = factor(id), group = interaction(id, type), color = type)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = my_pos) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = my_pos) +
    geom_point(aes(y = estimate), position = my_pos, size = 3) +
    facet_wrap(~eff_prob, scales = "free", ncol = 2) +
    theme(axis.title.x = element_blank(), axis.text.x = element_blank())


```

#### Coverage

```{r}

#CHECK THE COVERAGE 
summary <- rbind(summarise_brms(all_effects_logit),
                 summarise_brms(all_effects_logit_rslope),
      all_effects_lmer_splines,
      all_effects_lmer_splines_rslope,
      all_effects_lmer_simple,
      all_effects_lmer_simple_rslope) %>%
      mutate(effect = ifelse(eff_prob == 0.5, 0, NA), 
             covered = effect <= upper95 & effect >= lower95, 
             length = upper95 - lower95) %>%
    group_by(type, eff_prob) %>%
    summarise(coverage = mean(covered), 
              meanlength = mean(length),
              .groups = "drop") %>%            
    group_by(eff_prob) %>%                      
    mutate(RE = meanlength[type == "lmer4_simple"] / meanlength) %>%
    ungroup()

summary

```

## Default priors & Two questions

```{r}

#CHECK THE SCORE DISTRIBUTION OF THE CHOSEN QUESTION
questions_to_fit <- question_col_names[c(1,2)] #change the no. of questions here 


sim_scores <- purrr::map_dfr(questions_to_fit, function(current_question) {
                      purrr::map_dfr(
                        sims_null, 
                        ~ as.list(summary(as.factor(.x[[current_question]]))), 
                        .id = "sim_id"
                      ) %>%
                        mutate(question = current_question) %>%
                        select(question, everything())
                     }) %>%
          group_by(question) %>%
          select(-sim_id) %>%
          summarise(across(everything(), mean))


sim_scores
```

### Logit model (2)

```{r}
# #CALCULATE LOGIT FITS 
# logit_formula <- as.formula(paste0(
#     "mvbind(", paste0(questions_to_fit, collapse = ", "),
#     ") ~ 1 + alsfrs_dly_mnths*group + (1 | p | subject_id)"
# ))
# 
# fits_logit2 <- brm_parallel(
#     args_shared = list(formula = bf(logit_formula, family = cumulative()) + set_rescor(FALSE), 
#                                     adapt_delta = 0.95,
#                                     init = 0.1,
#                                     chains = 4,
#                                     iter = 3000,
#                                     warmup = 1000),
#     args_per_fit = args_per_fit,
#     cache_dir = cache_dir,
#     cache_fits = TRUE,
#     future.globals = FALSE)
# 
# lapply(fits_logit2, summary)

```

```{r}
# all_effects_logit2 <- purrr::map_df(1:length(eff_prob), 
#                              ~ data.frame(id = .x, type = "logit", eff_prob = eff_prob[.x], estimate = effects_logit(fits_logit2[[.x]])))
# 
# #dim(posterior_epred(fits_logit2[[1]], newdata = predict_data, re_formula = NA)) 
# # check the output of posterior_epred, does it compute the expected score dif correctly? 
```

```{r}

# plot_logit2 <- all_effects_logit2 %>%
#   mutate(eff_prob = factor(eff_prob)) %>%
#   ggplot(aes(x = eff_prob, group = id, y = estimate)) + 
#     geom_hline(yintercept = 0) +
#     stat_pointinterval(position = position_dodge(width = 0.3)) + 
#     #expand_limits(y = shared_range) +
#     ggtitle("Logit")
# plot_logit2
```

### Lme4 checks (2)

#### Simple (2)

```{r}

# FIT SIMPLE LMER MODEL
fits_lmer_simple2 <- purrr::map(sims_null, function(data_for_lmer) {
    data_for_lmer$alsfrs_sum_subset <-  rowSums(data_for_lmer[, questions_to_fit])
    lme4::lmer(alsfrs_sum_subset ~ 1 + alsfrs_dly_mnths*group+ (1 |subject_id), data = data_for_lmer)
})

```

```{r}
#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 

all_effects_lmer_simple2 <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_simple", eff_prob = eff_prob[.x], effects_lmer_simple(fits_lmer_simple2[[.x]]))))


```

```{r}


plot_lmer_simple2 <- all_effects_lmer_simple2 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 simple")

plot_lmer_simple2
```

#### Splines (2)

```{r}
# FIT LMER SPLINES MODEL
# already have the function get_spline_coef

fits_lmer_splines2 <- purrr::map(sims_null, function(data_for_lmer) {
    
    spline_data <- ns(data_for_lmer$alsfrs_dly_mnths, 2)
    data_for_lmer <- cbind(data_for_lmer,
                           get_spline_coeffs(data_for_lmer$alsfrs_dly_mnths))
    data_for_lmer$alsfrs_sum_subset <- rowSums(data_for_lmer[, questions_to_fit])
     
  lme4::lmer(alsfrs_sum_subset ~ 1 + dly_mnths_spline_1 * group
             + dly_mnths_spline_2 * group + (1 |subject_id), data = data_for_lmer)
})
```

```{r}

#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 
all_effects_lmer_splines2 <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_splines", eff_prob = eff_prob[.x], effects_lmer_splines(fits_lmer_splines2[[.x]]))))


```

```{r}
plot_lmer_splines2 <- all_effects_lmer_splines2 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 splines")

plot_lmer_splines2
```

### Joined (2)

```{r}
# 
# #JOINED PLOT
# 
# my_pos <- position_dodge(width = 0.5)
# 
# rbind(summarise_brms(all_effects_logit2),
#       all_effects_lmer_splines2,
#       all_effects_lmer_simple2) %>%
#     mutate(eff_prob = factor(eff_prob)) %>%
#   ggplot(aes(x = factor(id), group = interaction(id, type), color = type)) + 
#     geom_hline(yintercept = 0) +
#     geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = my_pos) +
#     geom_linerange(aes(ymin = lower95, ymax = upper95), position = my_pos) +
#     geom_point(aes(y = estimate), position = my_pos, size = 3) +
#     facet_wrap(~eff_prob, scales = "free", ncol = 2) +
#     theme(axis.title.x = element_blank(), axis.text.x = element_blank())
```

```{r}
# #CHECK THE COVERAGE 
# summary2 <- rbind(summarise_brms(all_effects_logit2),
#       all_effects_lmer_splines2,
#       all_effects_lmer_simple2) %>%
#       mutate(effect = ifelse(eff_prob == 0.5, 0, NA), 
#              covered = effect <= upper95 & effect >= lower95, 
#              length = upper95 - lower95) %>%
#     group_by(type, eff_prob) %>%
#     summarise(coverage = mean(covered), 
#               meanlength = mean(length),
#               .groups = "drop") %>%            
#     group_by(eff_prob) %>%                      
#     mutate(RE = meanlength[type == "lmer4_simple"] / meanlength) %>%
#     ungroup()
# 
# summary2
```

## Default priors & Five questions

```{r}
#CHECK THE SCORE DISTRIBUTION OF THE CHOSEN QUESTION
questions_to_fit <- question_col_names[c(1,2,3,4,5)] #change the no. of questions here 


sim_scores <- purrr::map_dfr(questions_to_fit, function(current_question) {
                      purrr::map_dfr(
                        sims_null, 
                        ~ as.list(summary(as.factor(.x[[current_question]]))), 
                        .id = "sim_id"
                      ) %>%
                        mutate(question = current_question) %>%
                        select(question, everything())
                     }) %>%
          group_by(question) %>%
          select(-sim_id) %>%
          summarise(across(everything(), mean))


sim_scores
```

### Logit model (5)

```{r}
#CALCULATE LOGIT FITS 
logit_formula <- as.formula(paste0(
    "mvbind(", paste0(questions_to_fit, collapse = ", "),
    ") ~ 1 + alsfrs_dly_mnths*group + (1 | p | subject_id)"
))

fits_logit5 <- brm_parallel(
    args_shared = list(formula = bf(logit_formula, family = cumulative()) + set_rescor(FALSE), 
                                    adapt_delta = 0.95,
                                    init = 0.1,
                                    chains = 4,
                                    iter = 3000,
                                    warmup = 1000),
    args_per_fit = args_per_fit,
    cache_dir = cache_dir,
    cache_fits = TRUE,
    future.globals = FALSE)

lapply(fits_logit5, summary)

all_effects_logit5 <- purrr::map_df(1:length(eff_prob), 
                             ~ data.frame(id = .x, type = "logit", eff_prob = eff_prob[.x], estimate = effects_logit(fits_logit5[[.x]])))

plot_logit5 <- all_effects_logit5 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id, y = estimate)) + 
    geom_hline(yintercept = 0) +
    stat_pointinterval(position = position_dodge(width = 0.3)) + 
    #expand_limits(y = shared_range) +
    ggtitle("Logit")

plot_logit5

```

### Lme4 checks (5)

**Simple (5)**

```{r}
# FIT SIMPLE LMER MODEL
fits_lmer_simple5 <- purrr::map(sims_null, function(data_for_lmer) {
    data_for_lmer$alsfrs_sum_subset <-  rowSums(data_for_lmer[, questions_to_fit])
    lme4::lmer(alsfrs_sum_subset ~ 1 + alsfrs_dly_mnths*group+ (1 |subject_id), data = data_for_lmer)
})


fits_lmer_simple5_rslope <- purrr::map(sims_null, function(data_for_lmer) {
    data_for_lmer$alsfrs_sum_subset <-  rowSums(data_for_lmer[, questions_to_fit])
    lme4::lmer(alsfrs_sum_subset ~ 1 + alsfrs_dly_mnths*group+ (1 + alsfrs_dly_mnths |subject_id), data = data_for_lmer)
})

#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 

all_effects_lmer_simple5 <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_simple", eff_prob = eff_prob[.x], effects_lmer_simple(fits_lmer_simple5[[.x]]))))


all_effects_lmer_simple5_rslope <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_simple_rslope", eff_prob = eff_prob[.x], effects_lmer_simple(fits_lmer_simple5_rslope[[.x]]))))


#PLOTS
plot_lmer_simple5 <- all_effects_lmer_simple5 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 simple")

plot_lmer_simple5


plot_lmer_simple5_rslope <- all_effects_lmer_simple5_rslope %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 simple")

plot_lmer_simple5_rslope

```

**Splines (5)**

```{r}
# FIT LMER SPLINES MODEL
# already have the function get_spline_coef

fits_lmer_splines5 <- purrr::map(sims_null, function(data_for_lmer) {
    
    spline_data <- ns(data_for_lmer$alsfrs_dly_mnths, 2)
    data_for_lmer <- cbind(data_for_lmer,
                           get_spline_coeffs(data_for_lmer$alsfrs_dly_mnths))
    data_for_lmer$alsfrs_sum_subset <- rowSums(data_for_lmer[, questions_to_fit])
     
  lme4::lmer(alsfrs_sum_subset ~ 1 + dly_mnths_spline_1 * group
             + dly_mnths_spline_2 * group + (1 |subject_id), data = data_for_lmer)
})


fits_lmer_splines5_rslope <- purrr::map(sims_null, function(data_for_lmer) {
    
    spline_data <- ns(data_for_lmer$alsfrs_dly_mnths, 2)
    data_for_lmer <- cbind(data_for_lmer,
                           get_spline_coeffs(data_for_lmer$alsfrs_dly_mnths))
    data_for_lmer$alsfrs_sum_subset <- rowSums(data_for_lmer[, questions_to_fit])
     
  lme4::lmer(alsfrs_sum_subset ~ 1 + dly_mnths_spline_1 * group
             + dly_mnths_spline_2 * group + (1 + alsfrs_dly_mnths |subject_id), data = data_for_lmer)
})

#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 
all_effects_lmer_splines5 <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_splines", eff_prob = eff_prob[.x], effects_lmer_splines(fits_lmer_splines5[[.x]]))))

all_effects_lmer_splines5_rslope <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_splines_rslope", eff_prob = eff_prob[.x], effects_lmer_splines(fits_lmer_splines5_rslope[[.x]]))))

#PLOTS
plot_lmer_splines5 <- all_effects_lmer_splines5 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 splines")

plot_lmer_splines5


plot_lmer_splines5_rslope <- all_effects_lmer_splines5_rslope %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 splines")

plot_lmer_splines5_rslope


```

### Joined (5)

```{r}

rbind(summarise_brms(all_effects_logit5),
      all_effects_lmer_splines5,
      all_effects_lmer_simple5) %>%
    mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = factor(id), group = interaction(id, type), color = type)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = my_pos) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = my_pos) +
    geom_point(aes(y = estimate), position = my_pos, size = 3) +
    facet_wrap(~eff_prob, scales = "free", ncol = 2) +
    theme(axis.title.x = element_blank(), axis.text.x = element_blank())

#CHECK THE COVERAGE 
summary5 <- rbind(summarise_brms(all_effects_logit5),
      all_effects_lmer_splines5_rslope,
      all_effects_lmer_splines5,
      all_effects_lmer_simple5_rslope,
      all_effects_lmer_simple5) %>%
      mutate(effect = ifelse(eff_prob == 0.5, 0, NA), 
             covered = effect <= upper95 & effect >= lower95, 
             length = upper95 - lower95) %>%
    group_by(type, eff_prob) %>%
    summarise(coverage = mean(covered), 
              meanlength = mean(length),
              .groups = "drop") %>%            
    group_by(eff_prob) %>%                      
    mutate(RE = meanlength[type == "lmer4_simple"] / meanlength) %>%
    ungroup()

summary5

```

## Default priors & Eight questions

```{r}
#CHECK THE SCORE DISTRIBUTION OF THE CHOSEN QUESTION
questions_to_fit <- question_col_names[1:8] #change the no. of questions here 


sim_scores <- purrr::map_dfr(questions_to_fit, function(current_question) {
                      purrr::map_dfr(
                        sims_null, 
                        ~ as.list(summary(as.factor(.x[[current_question]]))), 
                        .id = "sim_id"
                      ) %>%
                        mutate(question = current_question) %>%
                        select(question, everything())
                     }) %>%
          group_by(question) %>%
          select(-sim_id) %>%
          summarise(across(everything(), mean))


sim_scores
```

### Logit model (8)

```{r}

#CALCULATE LOGIT FITS 
logit_formula <- as.formula(paste0(
    "mvbind(", paste0(questions_to_fit, collapse = ", "),
    ") ~ 1 + alsfrs_dly_mnths*group + (1 | p | subject_id)"
))

fits_logit8 <- brm_parallel(
    args_shared = list(formula = bf(logit_formula, family = cumulative()) + set_rescor(FALSE), 
                                    adapt_delta = 0.95,
                                    init = 0.1,
                                    chains = 4,
                                    iter = 3000,
                                    warmup = 1000),
    args_per_fit = args_per_fit,
    cache_dir = cache_dir,
    cache_fits = TRUE,
    future.globals = FALSE)

lapply(fits_logit8, summary)

all_effects_logit8 <- purrr::map_df(1:length(eff_prob), 
                             ~ data.frame(id = .x, type = "logit", eff_prob = eff_prob[.x], estimate = effects_logit(fits_logit8[[.x]])))

plot_logit8 <- all_effects_logit8 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id, y = estimate)) + 
    geom_hline(yintercept = 0) +
    stat_pointinterval(position = position_dodge(width = 0.3)) + 
    #expand_limits(y = shared_range) +
    ggtitle("Logit")

plot_logit8
```

### Lme4 checks (8)

#### Simple (8)

```{r}
# FIT SIMPLE LMER MODEL
fits_lmer_simple8 <- purrr::map(sims_null, function(data_for_lmer) {
    data_for_lmer$alsfrs_sum_subset <-  rowSums(data_for_lmer[, questions_to_fit])
    lme4::lmer(alsfrs_sum_subset ~ 1 + alsfrs_dly_mnths*group+ (1 |subject_id), data = data_for_lmer)
})

#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 

all_effects_lmer_simple8 <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_simple", eff_prob = eff_prob[.x], effects_lmer_simple(fits_lmer_simple8[[.x]]))))

plot_lmer_simple8 <- all_effects_lmer_simple8 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 simple")

plot_lmer_simple8
```

#### Splines (8)

```{r}
# FIT LMER SPLINES MODEL
# already have the function get_spline_coef

fits_lmer_splines8 <- purrr::map(sims_null, function(data_for_lmer) {
    
    spline_data <- ns(data_for_lmer$alsfrs_dly_mnths, 2)
    data_for_lmer <- cbind(data_for_lmer,
                           get_spline_coeffs(data_for_lmer$alsfrs_dly_mnths))
    data_for_lmer$alsfrs_sum_subset <- rowSums(data_for_lmer[, questions_to_fit])
     
  lme4::lmer(alsfrs_sum_subset ~ 1 + dly_mnths_spline_1 * group
             + dly_mnths_spline_2 * group + (1 |subject_id), data = data_for_lmer)
})

#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 
all_effects_lmer_splines8 <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_splines", eff_prob = eff_prob[.x], effects_lmer_splines(fits_lmer_splines8[[.x]]))))

plot_lmer_splines8 <- all_effects_lmer_splines8 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 splines")

plot_lmer_splines8
```

### Joined (8)

```{r}
rbind(summarise_brms(all_effects_logit8),
      all_effects_lmer_splines8,
      all_effects_lmer_simple8) %>%
    mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = factor(id), group = interaction(id, type), color = type)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = my_pos) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = my_pos) +
    geom_point(aes(y = estimate), position = my_pos, size = 3) +
    facet_wrap(~eff_prob, scales = "free", ncol = 2) +
    theme(axis.title.x = element_blank(), axis.text.x = element_blank())

#CHECK THE COVERAGE 
summary8 <- rbind(summarise_brms(all_effects_logit8),
      all_effects_lmer_splines8,
      all_effects_lmer_simple8) %>%
      mutate(effect = ifelse(eff_prob == 0.5, 0, NA), 
             covered = effect <= upper95 & effect >= lower95, 
             length = upper95 - lower95) %>%
    group_by(type, eff_prob) %>%
    summarise(coverage = mean(covered), 
              meanlength = mean(length),
              .groups = "drop") %>%            
    group_by(eff_prob) %>%                      
    mutate(RE = meanlength[type == "lmer4_simple"] / meanlength) %>%
    ungroup()

summary8
```

## Default priors & All questions

```{r}
#CHECK THE SCORE DISTRIBUTION OF THE CHOSEN QUESTION
questions_to_fit <- question_col_names#change the no. of questions here 


sim_scores <- purrr::map_dfr(questions_to_fit, function(current_question) {
                      purrr::map_dfr(
                        sims_null, 
                        ~ as.list(summary(as.factor(.x[[current_question]]))), 
                        .id = "sim_id"
                      ) %>%
                        mutate(question = current_question) %>%
                        select(question, everything())
                     }) %>%
          group_by(question) %>%
          select(-sim_id) %>%
          summarise(across(everything(), mean))


sim_scores
```

### Logit model (All)

```{r}
#CALCULATE LOGIT FITS 
logit_formula <- as.formula(paste0(
    "mvbind(", paste0(questions_to_fit, collapse = ", "),
    ") ~ 1 + alsfrs_dly_mnths*group + (1 | p | subject_id)"
))


fits_logit12 <- brm_parallel(
    args_shared = list(formula = bf(logit_formula, family = cumulative()) + set_rescor(FALSE), 
                                    adapt_delta = 0.95,
                                    init = 0.1,
                                    chains = 3,
                                    iter = 3000,
                                    warmup = 1000),
    args_per_fit = args_per_fit,
    cache_dir = cache_dir,
    cache_fits = TRUE,
    future.globals = FALSE)



all_effects_logit12 <- purrr::map_df(1:length(eff_prob), 
                             ~ data.frame(id = .x, type = "logit", eff_prob = eff_prob[.x], estimate = effects_logit(fits_logit12[[.x]])))




plot_logit12 <- all_effects_logit12 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id, y = estimate)) + 
    geom_hline(yintercept = 0) +
    stat_pointinterval(position = position_dodge(width = 0.3)) + 
    #expand_limits(y = shared_range) +
    ggtitle("Logit")

plot_logit12
```

### Lme4 checks (All)

#### Simple (All)

```{r}
# FIT SIMPLE LMER MODEL
fits_lmer_simple12 <- purrr::map(sims_null, function(data_for_lmer) {
    data_for_lmer$alsfrs_sum_subset <-  rowSums(data_for_lmer[, questions_to_fit])
    lme4::lmer(alsfrs_sum_subset ~ 1 + alsfrs_dly_mnths*group+ (1 |subject_id), data = data_for_lmer)
})


fits_lmer_simple12_rslope <- purrr::map(sims_null, function(data_for_lmer) {
    data_for_lmer$alsfrs_sum_subset <-  rowSums(data_for_lmer[, questions_to_fit])
    lme4::lmer(alsfrs_sum_subset ~ 1 + alsfrs_dly_mnths*group+ (1 + alsfrs_dly_mnths |subject_id), data = data_for_lmer)
})

#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 

all_effects_lmer_simple12 <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_simple", eff_prob = eff_prob[.x], effects_lmer_simple(fits_lmer_simple12[[.x]]))))


all_effects_lmer_simple12_rslope <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_simple_rslope", eff_prob = eff_prob[.x], effects_lmer_simple(fits_lmer_simple12_rslope[[.x]]))))

plot_lmer_simple12 <- all_effects_lmer_simple12 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 simple")

plot_lmer_simple12
```

#### Splines (All)

```{r}
# FIT LMER SPLINES MODEL
# already have the function get_spline_coef

fits_lmer_splines12 <- purrr::map(sims_null, function(data_for_lmer) {
    
    spline_data <- ns(data_for_lmer$alsfrs_dly_mnths, 2)
    data_for_lmer <- cbind(data_for_lmer,
                           get_spline_coeffs(data_for_lmer$alsfrs_dly_mnths))
    data_for_lmer$alsfrs_sum_subset <- rowSums(data_for_lmer[, questions_to_fit])
     
  lme4::lmer(alsfrs_sum_subset ~ 1 + dly_mnths_spline_1 * group
             + dly_mnths_spline_2 * group + (1 |subject_id), data = data_for_lmer)
})


fits_lmer_splines12_rslope <- purrr::map(sims_null, function(data_for_lmer) {
    
    spline_data <- ns(data_for_lmer$alsfrs_dly_mnths, 2)
    data_for_lmer <- cbind(data_for_lmer,
                           get_spline_coeffs(data_for_lmer$alsfrs_dly_mnths))
    data_for_lmer$alsfrs_sum_subset <- rowSums(data_for_lmer[, questions_to_fit])
     
  lme4::lmer(alsfrs_sum_subset ~ 1 + dly_mnths_spline_1 * group
             + dly_mnths_spline_2 * group + (1 + alsfrs_dly_mnths |subject_id), data = data_for_lmer)
})


#COMPUTE THE EFFECTS AND ORGANIZE THEM IN A SINGLE DATAFRAME 
all_effects_lmer_splines12 <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_splines", eff_prob = eff_prob[.x], effects_lmer_splines(fits_lmer_splines12[[.x]]))))



all_effects_lmer_splines12_rslope <- purrr::map_df(1:length(eff_prob), 
                             ~ cbind(data.frame(id = .x, type = "lmer4_splines_rslope", eff_prob = eff_prob[.x], effects_lmer_splines(fits_lmer_splines12_rslope[[.x]]))))

#PLOTS
plot_lmer_splines12 <- all_effects_lmer_splines12 %>%
  mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = eff_prob, group = id)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = position_dodge(width = 0.3)) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = position_dodge(width = 0.3)) +
    geom_point(aes(y = estimate), position = position_dodge(width = 0.3), size = 3) +
    #expand_limits(y = shared_range) +
    ggtitle("Lme4 splines")

plot_lmer_splines12
```

### Joined (All)

```{r}
rbind(summarise_brms(all_effects_logit12),
      all_effects_lmer_splines12,
      all_effects_lmer_simple12) %>%
    mutate(eff_prob = factor(eff_prob)) %>%
  ggplot(aes(x = factor(id), group = interaction(id, type), color = type)) + 
    geom_hline(yintercept = 0) +
    geom_linerange(aes(ymin = lower50, ymax = upper50), size = 1.2, position = my_pos) +
    geom_linerange(aes(ymin = lower95, ymax = upper95), position = my_pos) +
    geom_point(aes(y = estimate), position = my_pos, size = 3) +
    facet_wrap(~eff_prob, scales = "free", ncol = 2) +
    theme(axis.title.x = element_blank(), axis.text.x = element_blank())

#CHECK THE COVERAGE 
summary12 <- rbind(summarise_brms(all_effects_logit12),
      all_effects_lmer_splines12_rslope,
      all_effects_lmer_splines12,
      all_effects_lmer_simple12_rslope,
      all_effects_lmer_simple12) %>%
      mutate(effect = ifelse(eff_prob == 0.5, 0, NA), 
             covered = effect <= upper95 & effect >= lower95, 
             length = upper95 - lower95) %>%
    group_by(type, eff_prob) %>%
    summarise(coverage = mean(covered), 
              meanlength = mean(length),
              .groups = "drop") %>%            
    group_by(eff_prob) %>%                      
    mutate(RE = meanlength[type == "lmer4_simple"] / meanlength) %>%
    ungroup()

summary12

```
